---
title: "Compare Ivy Schools"
author: "C"
date: "November 10, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#################################################################################################
## Load your required package libraries - just load all of these as default always and forever ##
#################################################################################################
```{r}
x <- c("plyr", "dplyr", "stringr", "lubridate", "jsonlite", "httr", "xml2", "rvest", "devtools", "ggmap", "networkD3", "RSelenium", "pageviews", "aRxiv", "twitteR", "streamR", "scales", "gridExtra","tm","wordcloud","RCurl","ROAuth","SnowballC")
lapply(x, require, ch = T)
```
##########################################################################
## Scrape the data off of wikipedia for Ivy Schools  for the year 2016 ##
#########################################################################
Set Package

```{r}
ls("package:pageviews")
```

Brown University
```{r}
brown_views <- article_pageviews(project = "en.wikipedia", article = "Brown University", user_type = "user", start = "2016010100", end = "2016111000")
```
Columbia University
```{r}
columbia_views <- article_pageviews(project = "en.wikipedia", article = "Columbia University", user_type = "user", start = "2016010100", end = "2016111000")
```
Cornell University
```{r}
cornell_views <- article_pageviews(project = "en.wikipedia", article = "Cornell University", user_type = "user", start = "2016010100", end = "2016111000")
```
Dartmouth College
```{r}
dartmouth_views <- article_pageviews(project = "en.wikipedia", article = "Dartmouth College", user_type = "user", start = "2016010100", end = "2016111000")
```
Harvard University
```{r}
harvard_views <- article_pageviews(project = "en.wikipedia", article = "Harvard University", user_type = "user", start = "2016010100", end = "2016111000")
```
University of Pennsylvania
```{r}
penn_views <- article_pageviews(project = "en.wikipedia", article = "University of Pennsylvania", user_type = "user", start = "2016010100", end = "2016111000")
```
Princeton University
```{r}
princeton_views <- article_pageviews(project = "en.wikipedia", article = "Princeton University", user_type = "user", start = "2016010100", end = "2016111000")
```
Yale University
```{r}
yale_views <- article_pageviews(project = "en.wikipedia", article = "Yale University", user_type = "user", start = "2016010100", end = "2016111000")
```

###############################################
## Add new school variable to data frames ##
###############################################
```{r}
brown_views$School = "Brown"
columbia_views$School = "Columbia University"
cornell_views$School = "Cornell University"
dartmouth_views$School = "Dartmouth College"
harvard_views$School = "Harvard University"
penn_views$School = "University of Pennsylvania"
princeton_views$School = "Princeton University"
yale_views$School = "Yale University"
```
###############################
## Bind Data Frames together ##
###############################
```{r}
df = rbind(brown_views, columbia_views, cornell_views, dartmouth_views, harvard_views, penn_views, princeton_views, yale_views)
df$timestamp = as.numeric(gsub("-","",as.character(df$date)))
```
##################
## Create Plots ##
##################
Line Graph with fill geom 

```{r}
ggplot(data = df, aes(date, views, color=School)) + geom_smooth() + geom_point(size=.8) + scale_y_log10()+
    scale_fill_hue(c=0, l=360) + labs(list(title = "Number of Ivy League Page Views on Wikipedia in 2016", x = "Date", y = "Number of Views (Daily)")) 
```

